Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex

As mentioned earlier, these are the same size and mixing conditions
used by \citet{Jon:97}.
Note that De Jong does allow a little bit more flexibility in the
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
accommodate larger block sizes.%
\footnote{Note that this is the main reason that we are presenting our
  results using general triangular-array notation: to allow for the
  means to change over time for comparison with \citepos{GoW:02} and
  \citepos{GoJ:03} results.}

>>>>

As mentioned earlier, these are the same size and mixing conditions
used by \citet{Jon:97}.
Note that De Jong does allow a little bit more flexibility in the
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
accommodate larger block sizes.%
\footnote{Note that this is one reason that we are presenting our
  results using general triangular-array notation: to allow for the
  means to change over time for comparison with \citepos{GoW:02} and
  \citepos{GoJ:03} results.}
